DATA 607 Project 1 - Chess Scores

### 2018-09-19 DATA607/Project_1.Rmd
Updated DATA 607 Project 1 Added in network graph analysis for the fun of it

>>>>

## Fun with the Data

I really enjoy graph theory and couldn't pass up the oportunity to create a network graph from this chess data.  I recently learned how to use the igraph library from DataCamp so I will practice my skills on this data.  This is beyond the scope of the project and is for the fun of it.

I want the graph to use the players names as the ids
```{r, warning=FALSE, message=FALSE}
library(igraph)

players_names_1 <- player_df %>%
  select(player_id, players_name)

players_names_2 <- player_df %>%
  rename(opponent = player_id,
         opponents_name = players_name) %>%
  select(opponent, opponents_name)

G <- matches %>%
  select(player_id, opponent) %>%
  merge(players_names_1) %>%
  merge(players_names_2) %>%
  select(players_name, opponents_name) %>%
  graph_from_data_frame(., directed = FALSE) %>%
  simplify()
```

Now that we have loaded up the data into a graph let's see who Gary Hua played
```{r}
neighbors(G, 'Gary Hua')
```

One last thing.  I want to see if any of the people who played Gary Hua played each other.  I want to visualize it.

```{r}
G_sub <- induced_subgraph(G, neighbors(G, 'Gary Hua'))
layout <- layout.reingold.tilford(G_sub, circular=T)
plot(G_sub, layout=layout, vertex.size=20, vertex.color='white', vertex.frame.color = 'cornflower blue')
```

It looks like Joel R Hendon and Dinh Dang Bui were the only two who played each other and Gary Hua.
